\documentclass[a4paper]{book}

\usepackage[parts]{classicthesis}

\title{\textsf{Supervised Machine Learning techniquest for quench detection in superconductors}}
\author{Alessandro Biagiotti}
\date{Academic Year 2023/2024}

\begin{document}

\frontmatter

\maketitle

\tableofcontents

\mainmatter

\chapter{An overview of superconductor quench}
Give a brief overview of what superconductor quench is.
\section{Superconductivity}
Give a brief overview of what superconductivity is at the microscopic level (London pairs,
interactions with the reticle, etc...)
\section{Type I superconductors}
Give a very rapid overview of what Type I superconductors are
\section{Type II superconductors}
Give insights about Type II superconductors
\chapter{An overview of the used machine learning models}
Chapter dedicated to a brief explanation of what machine learning is as well as the inner workings
of some of the used models.
\section{Supervised models}
An overview of what supervised models are
\subsection{DecisionTreeClassifier}
theoretical description of decision trees
\subsection{RandomForestClassifier}
theoretical description of random forests
\subsection{SVM}
theoretical description of SVMs
\section{Unsupervised models}
An overview of what unsupervised models are
\subsection{Clustering with k\-means}
An overview of k\-means clustering in theory
\chapter{The problem}
Section dedicated to talking about the problem
\section{Quench Recognition Problem (QRP)}
What do we expect from the Quench recognition problem? What are our labels?
\section{Quench Localization Problem (QLP)}
What do we expect from the Quench Localization problem? What are our labels?
\chapter{Solution for QRP}
A chapter entirely dedicated to the resolution of the QRP
\section{The data}
Description of the data and the labels.
\section{The models in Scikit\-learn?}
A brief description of the various models in Scikit\-learn
\section{TreeAggregator}
An overview of the Tree Aggregator structure
\section{Performance analysis}
Final performance analysis in which I show that among all of the possible models the best performing
seems to be the TA and I also show that they perform well in the blind test.
\chapter{Solution for QLP}
A chapter entirely dedicated to the resolution of the QLPo
\section{The data}
Description of the data and the labels.
\section{First approaches using Clustering}
\section{Extension of the QRP models to the new problem}
\section{Performance analysis}
\chapter{Further developmens and ideas}
\chapter{Conclusions}


%\addcontentsline{toc}{chapter}{List of Figures}
%\listoffigures
%\addcontentsline{toc}{chapter}{List of Tables}
%\listoftables
%
%\mainmatter
%
%\setcounter{chapter}{-1}
%\include{src/introduction}
%\include{src/context}
%\include{src/preliminaries}
%
%\part{On sweeping \texorpdfstring{$k$}{k}-limited automata}
%\include{src/techniques}
%\include{src/sweeplimited}
%\include{src/nondeterminism}
%
%\part{Other models}
%\include{src/unaryoncemarking}
%
%\appendix
%\cleardoublepage
%\part*{Appendix}
%\include{src/complresults}
%\include{src/constructions}
%
%\hfuzz=2pt
%\tolerance=257
%\printbibliography

\end{document}
